Removing footnotes and appendices

### 2022-01-26 data-cleaning/footnotes_appendix.Rmd
updated shortening text code #1

```{r}
# remove text after "summary of argument" if it exists
amicus <- amicus %>%
  mutate(txt_full = str_squish(txt_full),
         txt_short = case_when(
           id == 861820795454 ~ gsub(pattern = ".*summary \\[\\*9\\] of the argument", replacement = "",
                                     x = txt_full, ignore.case = TRUE),
           grepl("summary of argument|Summary of Argument|SUMMARY OF ARGUMENT", txt_full,
                 ignore.case = TRUE) ~
             gsub(pattern = ".*summary of argument|.*Summary of Argument|.*SUMMARY OF ARGUMENT",
                  replacement = "",
                  x = txt_full, ignore.case = TRUE),
           grepl("summary of the argument", txt_full, ignore.case = TRUE) ~
             gsub(pattern = ".*summary of the argument", replacement = "",
                  x = txt_full, ignore.case = TRUE),
           id == 861820908073 ~ gsub(pattern = ".*introduction and summary", replacement = "",
                                     x = txt_full, ignore.case = TRUE),
           id == 861820896073 ~ gsub(pattern = ".*introduction", replacement = "",
                                     x = txt_full, ignore.case = TRUE),
           id == 861822667487 ~ gsub(pattern = ".*introduction", replacement = "",
                                     x = txt_full, ignore.case = TRUE),
           #this line can be changed to T ~ '' once the raw brief file is updated
           T ~ txt_full),
         txt_short = str_squish(txt_short))
```

@@

Let's see how many documents have `APPENDIX A` in them.

```{r}
amicus <- amicus %>% filter(appendix_1a == 0) %>%
  mutate(appendix_a = str_count(txt_short, "APPENDIX A"))

@@

```{r}
amicus <- amicus %>% filter(appendix_1a == 0 & appendix_a == 0) %>% 
  mutate(appendix = str_count(txt_short, "APPENDIX"))

@@

There are 345 briefs that mention footnotes.

@@

@@

```{r}
a <- amicus %>% filter(footnotes_cor == 0 & footnotes_1 == 0) %>% 
  mutate(footnotes = str_count(txt_short, "footnotes"))

@@

There are 149 briefs remaining that mention `footnotes`.

>>>>

```{r}
# remove text after "summary of argument" if it exists
amicus <- amicus %>%
  mutate(txt_full = str_squish(txt_full),
         txt_short = case_when(
           id == 861820795454 ~ gsub(pattern = ".*summary \\[\\*9\\] of the argument", replacement = "",
                                     x = txt_full, ignore.case = TRUE),
           grepl("summary of argument|Summary of Argument|SUMMARY OF ARGUMENT", txt_full,
                 ignore.case = TRUE) ~
             gsub(pattern = ".*summary of argument|.*Summary of Argument|.*SUMMARY OF ARGUMENT",
                  replacement = "",
                  x = txt_full, ignore.case = TRUE),
           grepl("summary of the argument", txt_full, ignore.case = TRUE) ~
             gsub(pattern = ".*summary of the argument", replacement = "",
                  x = txt_full, ignore.case = TRUE),
           id == 861820908073 ~ gsub(pattern = ".*introduction and summary", replacement = "",
                                     x = txt_full, ignore.case = TRUE),
           id == 861820896073 ~ gsub(pattern = ".*introduction", replacement = "",
                                     x = txt_full, ignore.case = TRUE),
           id == 861822667487 ~ gsub(pattern = ".*introduction", replacement = "",
                                     x = txt_full, ignore.case = TRUE),
           T ~ ''),
         txt_short = str_squish(txt_short))
```

@@

Let's see how many documents have `APPENDIX A` in them.
```{r}
amicus$appendix_a <- ifelse(amicus$appendix_1a < 1, str_count(amicus$txt_short, "APPENDIX A"), 0)

@@

```{r}
amicus$appendix <- ifelse(amicus$appendix_1a < 1 & amicus$appendix_a < 1, 
                            str_count(amicus$txt_short, "APPENDIX"), 0)

@@

There are 352 briefs that mention footnotes.

@@

There also seems to be a pattern of `footnotes *` to reference the footnotes section. Let's see how many of this reference are in the briefs.

```{r}
amicus$footnotes_star <- ifelse(amicus$footnotes_cor < 1 & amicus$footnotes_1 < 1,
                                str_count(amicus$txt_short, "footnotes \\*"), 0)

table(amicus$footnotes_star)
```

There are 94 briefs that mention `footnotes *` where the footnotes have not yet been removed. We can remove all text after this string as well.

```{r}
amicus <- amicus %>% mutate(
         txt_short = case_when(
           grepl("footnotes \\*", txt_short) ~ 
             gsub(pattern = "footnotes \\*.*", replacement = "", x = txt_short),
           T ~ txt_short),
         txt_short = str_squish(txt_short))
```

Checking to make sure `footnotes *` references have been removed.

```{r}
a <- amicus %>%
  mutate(footnotes_star = str_count(txt_short, "footnotes \\*"))

table(a$footnotes_star)
```

@@

```{r}
a <- amicus %>% filter(footnotes_cor == 0 & footnotes_1 == 0 & footnotes_star == 0 &
                        appendix_1a == 0 & appendix_a == 0 & appendix == 0) %>% 
  mutate(footnotes = str_count(txt_short, "footnotes"))

@@

There are 47 briefs remaining that mention `footnotes`.

Now let's see how many remaining briefs mention appendices.

```{r}
a <- amicus %>% filter(appendix_1a == 0 & appendix_a == 0 & appendix == 0) %>% 
   mutate(appendix_all = str_count(txt_short, "appendix"))

table(a$appendix_all)
```

There are only 52 briefs remaining that mention an appendix that have not already had their appendix removed.

Hoe many briefs had neither an appendix or footnotes removed?

```{r}
amicus %>% filter(appendix_1a == 0 & appendix_a == 0 & appendix == 0 &
                   footnotes_cor == 0 & footnotes_1 == 0 & footnotes_star == 0) %>% count()
```
253 briefs had neither an appendix or footnotes removed.

Now we want to save the new shortened version of the text into a csv.

```{r}
#amicus <- amicus %>% select(case, brief, id, txt_short)

#box_write(amicus,
#          file_name = "shortened-amicus-brief-text.csv",
#          dir_id = 145990409196)
```
